---
title: "EcoleInt_IDC2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Checking data
```{r, include=FALSE}
library(readr)
library(ggpubr)
library(plyr)

########################### Functions
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}

##########################################################################

################ DATA PREP
day1_df <-
  read_csv("all_correction_status_Day1_within.csv",
    col_types = cols(
      Book_Level = col_factor(levels = c("High", "Low")),
      Correction_Status = col_factor(levels = c("Corrected",
                                                "Not_Corrected")),
      Exp_Day = col_factor(levels = c("D1",
                                      "D2")),
      Mistake_Type = col_factor(levels = c("T1",
                                           "T2", "T3", "T4")),
      Robot_Hand_Condition = col_factor(levels = c("Pointing",
                                                   "Not_Pointing"))
    )
  )

day2_df <-
  read_csv("all_correction_status_Day2_within.csv",
    col_types = cols(
      Book_Level = col_factor(levels = c("High", "Low")),
      Correction_Status = col_factor(levels = c("Corrected",
                                                "Not_Corrected")),
      Exp_Day = col_factor(levels = c("D1",
                                      "D2")),
      Mistake_Type = col_factor(levels = c("T1",
                                           "T2", "T3", "T4")),
      Robot_Hand_Condition = col_factor(levels = c("Pointing",
                                                   "Not_Pointing"))
    )
  )

day2_df = subset(day2_df, !(day2_df$Correct_Word %in% c("properly", "right", "run", "ran", "fight")), na.rm=T)
df <- rbind(day1_df,day2_df)

```
### Correct per day
```{r}

res = table(df$Exp_Day, df$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Experiment Day", ylab = "Correction Percentage")
              #label = TRUE, lab.col = "white", lab.pos = "in")
p
```
There is an effect of the day on the correction with higher number of corrections in D1! :(

### Correct per type
```{r}
res = table(df$Mistake_Type, df$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired")
p

```
```{r}
res = table(df$Mistake_Type_2, df$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Type of Mistake", ylab = "Correction Percentage")
p

```
```{r}
df_point = subset(df,df$Robot_Hand_Condition == "Pointing")
res = table(df_point$Mistake_Type_2, df_point$Correction_Status) 
res = prop.table(res,1)*100
res

df_not = subset(df,df$Robot_Hand_Condition == "Not_Pointing")
res2 = table(df_not$Mistake_Type_2, df_not$Correction_Status) 
res2 = prop.table(res2,1)*100

chisq.test(res) 
chisq.test(res2) 
res = data.frame(res)
res["Hand"] <- "Pointing"
res2 = data.frame(res2)
res2["Hand"] <- "Not_Pointing"
res3 <- rbind(res,res2)
res3$Var2 <- as.character(res3$Var2)
res3$Var2 <- factor(res3$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res3, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Type of Mistake", ylab = "Correction Percentage")
facet(p, facet.by="Hand")


```

```{r}
df_low = subset(df,df$Book_Level == "Low")
df_point = subset(df_low,df$Robot_Hand_Condition == "Pointing")
res = table(df_point$Mistake_Type_2, df_point$Correction_Status) 
res = prop.table(res,1)*100
res

df_not = subset(df,df$Robot_Hand_Condition == "Not_Pointing")
res2 = table(df_not$Mistake_Type_2, df_not$Correction_Status) 
res2 = prop.table(res2,1)*100

chisq.test(res) 
chisq.test(res2) 
res = data.frame(res)
res["Hand"] <- "Pointing"
res2 = data.frame(res2)
res2["Hand"] <- "Not_Pointing"
res3 <- rbind(res,res2)
res3$Var2 <- as.character(res3$Var2)
res3$Var2 <- factor(res3$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res3, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Type of Mistake", ylab = "Correction Percentage")
facet(p, facet.by="Hand")


```

```{r}
df_high = subset(df,df$Book_Level == "High")
df_point = subset(df_high,df$Robot_Hand_Condition == "Pointing")
res = table(df_point$Mistake_Type_2, df_point$Correction_Status) 
res = prop.table(res,1)*100
res

df_not = subset(df,df$Robot_Hand_Condition == "Not_Pointing")
res2 = table(df_not$Mistake_Type_2, df_not$Correction_Status) 
res2 = prop.table(res2,1)*100

chisq.test(res) 
chisq.test(res2) 
res = data.frame(res)
res["Hand"] <- "Pointing"
res2 = data.frame(res2)
res2["Hand"] <- "Not_Pointing"
res3 <- rbind(res,res2)
res3$Var2 <- as.character(res3$Var2)
res3$Var2 <- factor(res3$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res3, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Type of Mistake", ylab = "Correction Percentage")
facet(p, facet.by="Hand")


```

# Low
```{r}
df_low = subset(df,df$Book_Level == "Low")
res = table(df_low$Mistake_Type_2, df_low$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Type of Mistake", ylab = "Correction Percentage")
p

```

# High
```{r}
df_low = subset(df,df$Book_Level == "High")
res = table(df_low$Mistake_Type_2, df_low$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Type of Mistake", ylab = "Correction Percentage")
p

```


### Correct per mistake order
```{r}
res = table(df$Mistake_Order, df$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Mistake Order", ylab = "Correction Percentage")
p

```

### Correct per book
```{r}
res = table(df$Book_Level, df$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Book Level", ylab = "Correction Percentage")
p
```

# STAT TEST
## Test pointing effect on all children
```{r}
res = table(df$Robot_Hand_Condition, df$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Robot Hand Condition", ylab = "Correction Percentage")
p 
```
## Test pointing effect on low level kids
```{r}
df_low = subset(df,df$Book_Level == "Low")
res = table(df_low$Robot_Hand_Condition, df_low$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Robot Hand Condition", ylab = "Correction Percentage")
p
```

## Test pointing effect on high level kids
```{r}
df_high = subset(df,df$Book_Level == "High")
res = table(df_high$Robot_Hand_Condition, df_high$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
res = data.frame(res)
res$Var2 <- as.character(res$Var2)
res$Var2 <- factor(res$Var2, levels=c("Not_Corrected", "Corrected"))
p = ggbarplot(res, x = "Var1", y = "Freq", 
              fill = "Var2", color = "Var2", palette = "Paired",
              xlab = "Robot Hand Condition", ylab = "Correction Percentage")
p
```
#### Test pointing effect for each type of mistakes
###### T1
```{r}
df_t1 = subset(df,df$Mistake_Type == "T1")
res = table(df_t1$Robot_Hand_Condition, df_t1$Correction_Status) 
res
```
###### T2
```{r}
df_t2 = subset(df,df$Mistake_Type == "T2")
res = table(df_t2$Robot_Hand_Condition, df_t2$Correction_Status) 
res
chisq.test(res) 
```
###### T3
```{r}
df_t3 = subset(df,df$Mistake_Type == "T3")
res = table(df_t3$Robot_Hand_Condition, df_t3$Correction_Status) 
res
chisq.test(res) 
```
###### T4
```{r}
df_t4 = subset(df,df$Mistake_Type == "T4")
res = table(df_t4$Robot_Hand_Condition, df_t4$Correction_Status) 
res
chisq.test(res) 
```
##### Test pointing effect according to Mistake_Type_2
###### Type-1
```{r}
df_type1 = subset(df,df$Mistake_Type_2 == "Type-1")
res = table(df_type1$Robot_Hand_Condition, df_type1$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
```
###### S2
```{r}
df_type3 = subset(df,df$Mistake_Type_2 == "Type-3")
res = table(df_type3$Robot_Hand_Condition, df_type3$Correction_Status) 
res = prop.table(res,1)*100
chisq.test(res) 
```
###### Type-2
```{r}
df_type2 = subset(df,df$Mistake_Type_2 == "Type-2")
res = table(df_type2$Robot_Hand_Condition, df_type2$Correction_Status) 
res = prop.table(res,1)*100
chisq.test(res) 
```

##### Test pointing effect according to Mistake_Type_2 
###### Low
### Typ1-1 and Low
```{r}
df_type1 = subset(df,df$Mistake_Type_2 == "Typ1-1" & df$Book_Level == "Low")
res = table(df_type1$Robot_Hand_Condition, df_type1$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res) 
```
### Type-3 and Low
```{r}
df_type3 = subset(df,df$Mistake_Type_2 == "Type-3" & df$Book_Level == "Low")
res = table(df_type3$Robot_Hand_Condition, df_type3$Correction_Status) 
res = prop.table(res,1)*100
chisq.test(res) 
```
### Type-2 and Low
```{r}
df_type2 = subset(df,df$Mistake_Type_2 == "Type-2" & df$Book_Level == "Low")
res = table(df_type2$Robot_Hand_Condition, df_type2$Correction_Status) 
res = prop.table(res,1)*100
chisq.test(res) 
```
###### High
### Typ1-1 and High
```{r}
df_type1 = subset(df,df$Mistake_Type_2 == "Typ1-1" & df$Book_Level == "High")
res = table(df_type1$Robot_Hand_Condition, df_type1$Correction_Status) 
res = prop.table(res,1)*100
res
chisq.test(res)
```
### Type-3 and High
```{r}
df_type3 = subset(df,df$Mistake_Type_2 == "Type-3" & df$Book_Level == "High")
res = table(df_type3$Robot_Hand_Condition, df_type3$Correction_Status) 
res = prop.table(res,1)*100
chisq.test(res) 
```
### Type-2 and High
```{r}
df_type2 = subset(df,df$Mistake_Type_2 == "Type-2" & df$Book_Level == "High")
res = table(df_type2$Robot_Hand_Condition, df_type2$Correction_Status) 
res = prop.table(res,1)*100
chisq.test(res) 
```
